Adaption of the Chumbley Score to matching of bullet striation marks

### 2018-03-18 doc/paper.Rmd
change of figure 2

```{r win-comparison, fig.width=8, fig.height=5, out.width='\\textwidth', fig.cap=" The two plots on the left show how the same shift behaves in case of a matching pair and the two plots on the right show how the different shift behaves in case of a matching pair."}

>>>>

```{r win-comparison, warning=FALSE, fig.width=8, fig.height=3.5, fig.cap="In- and out-of-phase samples from two markings created by the same source. On the left, sample windows are in-phase, on the right the pairs of sampled windows are out-of-phase. Note that for convenience, the markings are moved into phase on the left and out-of phase on the right. The Chumbley-score is based on a Mann-Whitney U test of the correlations derived from these two sets."}
sigs_graphics <- readRDS("../data/sigs_generate_window.rds")
sigs_graphics$sigs_land_id_1_match <- sigs_graphics$sigs_land_id_1_match %>% group_by(land_id) %>% mutate(y = y-min(y, na.rm=T))

# Matching signature
d1<- sigs_graphics.match[which(sigs_graphics.match$land_id==1,arr.ind = TRUE),]
d2<- sigs_graphics.match[which(sigs_graphics.match$land_id==276,arr.ind = TRUE),]
data1<-d1 %>%select(l30)
#data1<- data1$y
data2<- d2 %>%select(l30)
#data2<- data2$y
window_opt = 120 
window_val = 50
coarse = 1
data1<- matrix(unlist(data1))
data2<- matrix(unlist(data2))

sigs1.min = sigs_graphics[[1]] %>% filter(land_id==1) %>% select(y) %>% min()
sigs2.min = sigs_graphics[[1]] %>% filter(land_id==276) %>% select(y) %>% min()
window_val <- 3*window_val*0.645

same.shift <- -(365-338)*1/.645 + sigs2.min - sigs1.min 
xs <- seq(100, 1800, length=10)
rects <- data.frame(ymin=-Inf, ymax= Inf, xmin = xs, xmax = xs+window_val)

p1 <- sigs_graphics[[1]] %>% filter(land_id %in% c(1, 276)) %>% 
  ggplot() + 
  geom_segment(aes(x = xmin, y=ymin, xend = xmin, yend=ymax), 
               colour="grey50", linetype=3, data = rects) +
  geom_segment(aes(x = xmax, y=ymin, xend = xmax, yend=ymax), 
               colour="grey50", linetype=3, data = rects) +
  geom_rect(aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax), 
            data=rects, fill= "grey90") +
  geom_line(aes(x = y-same.shift*I(land_id==276), 
                y=l30-5*I(land_id==276), group=land_id)) + 
  theme_bw() +
  theme(axis.title.y = element_blank(), 
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  xlab("Relative Location (in microns)") +
  ggtitle("In-phase sample")

diff.shift <- -(365-338)*1/.645 + sigs2.min - sigs1.min + 70

p2 <- sigs_graphics[[1]] %>% filter(land_id %in% c(1, 276)) %>% 
  ggplot() + 
  geom_segment(aes(x = xmin, y=ymin, xend = xmin, yend=ymax), 
               colour="grey50", linetype=3, data = rects) +
  geom_segment(aes(x = xmax, y=ymin, xend = xmax, yend=ymax), 
               colour="grey50", linetype=3, data = rects) +
  geom_rect(aes(xmin=xmin, xmax=xmax, ymin=ymin, ymax=ymax), 
            data=rects, fill= "grey90") +
  geom_line(aes(x = y-diff.shift*I(land_id==276), 
                y=l30-5*I(land_id==276), group=land_id)) + 
  theme_bw() +
  theme(axis.title.y = element_blank(), 
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank()) +
  xlab("Relative Location (in microns)") +
  ggtitle("Out-of-phase sample")

library(gridExtra)
grid.arrange(p1,p2, ncol=2)
```

```{r win-comparison-2, fig.width=8, fig.height=5, out.width='\\textwidth', fig.cap=" The two plots on the left show how the same shift behaves in case of a matching pair and the two plots on the right show how the different shift behaves in case of a matching pair.", eval=FALSE}
